|

### 2024-09-07 manuscript/appendix1.Rmd
files up to date
arranged appendix1

output: 
  word_document:
    reference_docx: Chapter2-styles-appendix.docx
    fig_caption: yes
csl: ecology.csl
---

```{r setup, include = FALSE}

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(data.table)
library(brms)
library(flextable)
library(officer)
library(dplyr)

@@

```{r figS1, out.width = "100%", fig.cap = "**Figure S1.** Among individual differences in the development of hunting expertise in the model where we do not account for prey speed and average rank. The predators' hunting success (i.e. the probability of capturing the four prey) is on the y axis, and the predators' cumulative experience (i.e. the number of matches played prior to each observation) is on the x axis. Each fitted curve represents an individual predator. The individual curves are separated by differences between their first and last predicted value, and displayed as such in three distinct panels. (A) Individuals with a >0.5 unit increase in hunting success with experience (B) Individuals with a <-0.5 unit decrease in hunting success with experience. (C) Individuals that maintained a stable hunting success (between -0.5 and 0.5 unit change in hunting success)"}

knitr::include_graphics(
  here::here(
    "outputs", "04_outputs_figures",
    "appendix1_figureS1.png"
  )
)

```{r figS2, out.width = "100%", fig.cap = "**Figure S2.** Correlations between the predators' mean hunting success (y axis) and intra individual variance in speed (x axis) to test for differences in success between individuals along the flexible-specialist hunter continuum. Each point represents the posterior median predicted value of an individual predator along with its 95% HPD interval. Individuals with lower IIV are specialist hunters, while individuals with higher IIV are flexible hunters. (A) Correlation when predators were novice (B) Correlation when predators were advanced"}

>>>>

output: 
  word_document:
    reference_docx: appendix-styles.docx
    fig_caption: yes
csl: ecology.csl
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(data.table)
library(brms)
library(flextable)
library(officer)
library(dplyr)
```

@@

```{r figS1, out.width = "100%", fig.cap = "**Figure S1.** Correlations between the predators' mean hunting success (y axis) and intra individual variance in speed (x axis) to test for differences in success between individuals along the flexible-specialist hunter continuum. Each point represents the posterior median predicted value of an individual predator along with its 95% HPD interval. Individuals with lower IIV are specialist hunters, while individuals with higher IIV are flexible hunters. (A) Correlation when predators were novice (B) Correlation when predators were advanced"}
